%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Developer CV
%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[9pt]{developercv} % Default font size, values from 8-12pt are recommended
\usepackage{multicol}
\setlength{\columnsep}{0mm}
%----------------------------------------------------------------------------------------
\usepackage{lipsum}  


\begin{document}

%----------------------------------------------------------------------------------------
%	TITLE AND CONTACT INFORMATION
%----------------------------------------------------------------------------------------

\begin{minipage}[t]{0.5\textwidth} 
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	
	{ \fontsize{16}{20} \textcolor{black}{\textbf{\MakeUppercase{Andrey Otvagin}}}} % First name
	
	\vspace{6pt}
    \icon{Envelope}{11}{\href{mailto:otvagin@ucsb.edu}{otvagin@ucsb.edu}}
    \hspace{12pt}

    \icon{Github}{11}{\href{https://github.com/an0tv}{github.com/an0tv}}
    \hspace{12pt}
    
    \icon{Chain}{11}{\href{https://an0tv.github.io/}{an0tv.github.io}}
    \hspace{12pt}

    
\end{minipage}
\hfill
\begin{minipage}[t]{0.5\textwidth}
    \vspace{-18pt}
    \cvsect{Skills}
    \vspace{-6pt}
    
    \begin{minipage}[t]{0.2\textwidth}
        \textbf{Languages:}
    \end{minipage}
    \hfill
    \begin{minipage}[t]{0.73\textwidth}
        C, C++, Python, ASM, SystemVerilog, VHDL, R
    \end{minipage}
    \vspace{4mm}
    
    \begin{minipage}[t]{0.2\textwidth}
        \textbf{Technologies:}
    \end{minipage}
    \hfill
    \begin{minipage}[t]{0.73\textwidth}
        Docker, Git, Eclipse Mosquitto, WSL, OpenOCD, KiCad, Altium, ModelSim, LTspice, Logisim-Evolution, 
    \end{minipage}
    
\end{minipage}


%----------------------------------------------------------------------------------------
%	EDUCATION
%----------------------------------------------------------------------------------------
\vspace{-4 pt}
\cvsect{Education}
\begin{entrylist}

\vspace{-4pt}

    \entry
    {}
    {University of California, Santa Barbara}
    {September 2025 – June 2027}
    {M.S. Computer Engineer
    \begin{itemize}[noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt, leftmargin=10pt]
        \item Focus: Computer Architecture \& VLSI
    \end{itemize}}
    \entry
    {}
    {University of California, Santa Barbara}
    {September 2022 – June 2026}
    {B.S. Computer Engineering
    \begin{itemize}[noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt, leftmargin=10pt]
        \item Relevant Coursework: Deep Learning, Advanced Computer Architecture, Data Structures \& Algorithms, Embedded System, Machine Learning, Circuits, VLSI
    \end{itemize}}

    \entry
    {}
    {University of California, Santa Barbara}
    {September 2022 – June 2026}
    {B.S. Statistics \& Data Science 
    \begin{itemize}[noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt, leftmargin=10pt]
        \item Relevant Coursework: SAS Programming, SQL, Advanced Statistical Models, Survival Analysis, Stochastic Processes, Statistical Machine Learning, Regression Analysis, Advanced Linear Algebra
    \end{itemize}}
    
\end{entrylist}

%----------------------------------------------------------------------------------------
%	EXPERIENCE
%----------------------------------------------------------------------------------------
\vspace{-14 pt}
\cvsect{Experience}
\begin{entrylist}
    \entry
        {}
        {Becton Dickinson Bioscience - Firmware R\&D Engineer}
        {June 2024 – Present}
        {\vspace{-8pt}
        \begin{itemize}[noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt, leftmargin=10pt]
            \item Developed Hardware and Software for HOOTL and HITL test suite for embedded systems. 
            \item Optimized system responsiveness by designing timeout strategies for long-running processes, enhancing overall system reliability. 
            \item Deployed a build pipeline to allow for nightly firmware builds for embedded subsystems.  
            \item Created thread-safe asynchronous fault monitoring system for embedded linux environment. 
        \end{itemize}}
    \entry
        {}
        {Gaucho Racing (UCSB Formula SAE) - Electronics \& Data Lead}
        {September 2022 – Present}
        {\vspace{-8pt}
        \begin{itemize}[noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt, leftmargin=10pt]
            \item Led development of SAM, a high-throughput sensor array module for automotive systems, enabling versatile data collection including tire and rotor temperature, push-rod force, ride height, and vehicle dynamics monitoring via EKF with differential GPS and accelerometers.
            \item Deployed a real-time data collection \& analytics system on Jetson Orin Nano to monitor data streamed by SAM through a custom CAN \& CANFD protocol translator, allowing for real-time thermal prediction and anomaly detection. 
            \item Engineered a custom CAN protocol with built-in system prioritization, ensuring reliable communication under high bus load. 
            \item Helped develop a firmware monorepo to strive for architecture agnostic development as well as easier build pipeline implementation for HOOTL testing. 
            \item Implemented CI/CD pipelines for a HOOTL system, accelerating development and reducing integration friction.
            \item Promoted collaborative coding practices and knowledge sharing within the team through
            extensive documentation.
            \item Coordinated closely with the mechanical and aerodynamic teams for better hardware integration into respective assemblies.  
            
        \end{itemize}}
\end{entrylist}

%----------------------------------------------------------------------------------------
%	Projects
%----------------------------------------------------------------------------------------
\vspace{-14 pt}
\cvsect{Projects}
\begin{entrylist}
    \entry
    {}
    {RISC Processor}
    {Spring 2025}
    {\vspace{-8pt}
    \begin{itemize}[noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt, leftmargin=10pt]
    \item Created a pipelined RISC-V processor in verilog.
    \item Implementation features: 
        \begin{itemize}[noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt,leftmargin=10pt]
            \item Hazard Detection with respective forwarding and flushing.
            \item Branch Prediction implemented with  5-bit GHR, 2-bit PHT (32 entries), and 32-entry BTB. 
            \item Cache emulation with Hardware Prefetcher as well as Critical Word First and Early Restart.
            \item Superscalar implemeted via doubling the stages in the pipeline and modifying hazard and forwarding to cover cross pipeline forwarding as well as single branch execution.
        \end{itemize}
    \end{itemize}
    }

    \entry
    {}
    {SAM}
    {Fall 2024 - Present}
    {\vspace{-8pt}
    \begin{itemize}[noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt, leftmargin=10pt]
    \item Created an alternative to a Teensy 4.1 using an STM32G4 with a focus on automotive usage.
    \item Designed a compatible set of submodules for SAE vehicle characterization, meant for dynamic testing.
    \item Features:    
        \begin{itemize}[noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt, leftmargin=10pt]
            \item Dual CAN-FD transceivers.
            \item Buffered 2.048V reference.
            \item On-board programmer \& debugger via USB-C.
            \item 7-17V to 5V buck and 5V to 3.3V linear regulator.
            \item LP filter for 3.3VA as well as adjustable voltage reference source. 
            \item Small package (71mm * 23mm)
        \end{itemize}
    \end{itemize}
    }
    
\end{entrylist}

\end{document}
